\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Physical Nutrients}
\author{Hannah Gallagher}
\date{May 2020}

\begin{document}

\maketitle
\section*{Disclaimer}
This is just an online recipe book I've been adding to out of boredom and that I did not want to have constant ads whenever I cooked something. If you have a cool recipe to add to it. Let me know! This may be not the type of nutrients you want or need. Some of these foods are acquired tastes or simply what I'm cooking on a budget so I can buy more important things...i.e. education.  
\section*{Bare Essentials}
If you're broke this is my version of a Ramen budget with less additives. 
Oatmeal and skim milk for breakfast \\ 
Some bitter super green that no one else wants to eat as a salad for lunch \\ 
Family pack of mushrooms, Russell potatoes, Hunt's tomato paste, garlic, hot peppers, family pack of Wegman's chicken or pork (freeze -3), any array of those 99 cent beans. Make your own sourdough with proper unrefined flour...scale not necessary but fun.\\ 
Tangerines or store brand ice cream for dessert. 
\section*{Privileged broke in a pandemic and wanting to maintain an apartment move to dc and afford a house with a down payment and vacations with whatever boyfriend I get}

Chicken defrosted and marinated in balsamic vinegar.
Beans many garbanzo and kidney beans in red sauce. 

\section*{The rest}

\section*{Ingredients}
When I'm older with more knowledge and money, these are the items I'd always like to have on hand.

\begin{table}
\begin{tabular}{lllll}
Vegetables & Fruits & Dairy & Meat & Snacks \\
Eggplant   & Pomegranate & Eggs & Oyster & Pringles \\
Zucchini   & Banana  & Milk & Shrimp & Dark Chocolate \\
Mushroom   & Orange & Kefir & Pork Chop & Saltines \\ 
Carrot    & Blueberry & Yogurt & Sardines & Cheez-it \\

\end{tabular}
\end{table}

ehh well I've cut out red meat so far...spinach to offset that. 


\section*{Breakfast}

\subsection*{Eggs}
Make a quick x of oil onto a small nonstick pan. Quickly and not at all delicately crack the egg. Break the egg along the line and into the pan. Turn the heat down and move the egg around a little to make sure it does not stick.   

\subsection*{Yogurt}

\subsection*{Banana}
Grab a banana and worry about breakfast later.

\section*{Lunch}

\subsection*{Salad}
Chopped tomatoes, walnuts, cranberries, a kale leaf, and the rest romaine. 
\section*{Friends and Family Recipes}
\section*{Dinner Meats}

\subsection*{Pork Chops}

\subsection*{Chicken}

\subsection*{Shrimp}

\subsection*{Fish}
Oil and whole wheat flour then Trader Joe's mushroom co. blend. The type of thing to have white wine with or cook with. Maybe cherry tomatoes and some pasta or risotto too. 

\section{Dinner Soups} 

\subsection*{Miso Soup}

\subsection*{Stir Fry}
Bok Choy, sesame oil, soy sauce, egg, garlic, mushroom 
\section*{Snacks}


\section*{Food with friends}

\subsection*{Potato Skins} 
Meant to share with friends, but good either way. \\

Microwave the potato halfway and poke with fork. The halfway is to make sure the potato is not too fragile that when you're carving out the basin the potato doesn't break. Let cool...ideally do something else...start defrosting and cooking the bacon usually...use a spoon to carve and make the shape. \\ 
Place carved thin potatoes on a cookie sheet with foil to avoid a mess. \\
In a tiny bowl or mug, put olive oil (or whatever butter), garlic, array of spices and maplewood smoke spice. Baste the outside and inside of potato with this coating. 

Cut up a ton of chives (green onions) into half the potato group. \\ 
The other half of the potato group put a moderate amount of chives and replace with "Wegman's shredded Mexican cheese" pretty sure it's cheddar and mozzarella. \\ 
Put in the oven to get the process started. The cheese will melt down for the bacon to be added. Then once that is taken care of put more cheese on top of the bacon. \\ 



\section*{Weird Health Drinks}

\subsection*{Witches Brew} 
For when your sinuses are clogged. \\ 
Chop up a medium size onion, squeeze a quarter cup of lemon juice, that's the main part then strain it in whatever you want. I use my French press out of not wanting to buy something else. I'll usually add some green or breakfast tea to mask the taste of the onion since it's a lot to get used to. 

\subsection*{Carrot Juice} 

\subsection*{Green Juice}
Collards, frozen banana, almond milk 

\section*{Budget Recipes}

\subsection*{Hummus}
Garbanzo beans...to paste...Lemon Juice, garlic, cumin, salt, olive oil (extras...red pepper flakes, pine nuts, olives)
Good with carrots or bell peppers.
\end{document}
